---
title: "R-omics"
author: "terkaaa"
date: "22 lipca 2015"
output: html_document
---

# Introduction
This is an R-markdown document storing my experience from Summer Institute in Statistical Genetics [SISG](http://www.biostat.washington.edu/suminst/sisg/general).

In summer 2015, I participated in 6 modules offered during the workshop:

*  Probability and Statistical Inference
*  Gene Expression Profiling
*  Quantitative Genetics
*  Unsupervised Methods for Statistical Machine Learning
*  Reproducible Research in Biomedical Big Data
*  Pathway & Network Analysis for Omics Data

# The modules' content

## Probability and Statistical Inference

## Gene Expression Profiling

## Quantitative Genetics

## Unsupervised Methods for Statistical Machine Learning

## Reproducible Research in Biomedical Big Data

## Pathway & Network Analysis for Omics Data

Although quite tool-oriented in comparison with content of the other workshops, it was a priceless lesson for an R- beginner. I learned how to

1. Properly document and store my files
2. Build R packages
3. Describe my R functions
4. Upload my data on GitHub
5. Share my data in a smart way

As an example of what helpful tools did I learn, I would like to mention R packages: 

* roxygen2, which helps to describe functions
* devtools, which helps to build packages
* knitr, which builds smart documentation files like this one
* rmarkdown, R-friendly text editor

To install packages, follow the code:
``` {r}
#install.packages("devtools")
#install.packages("knitr")
#install.packages("roxygen2")
#install.packages("rmarkdown")
```
And then invoke them by typing:
``` {r}
#library(devtools) # same for other libraries
```

As for other documentation of what we learned, visit my [GitHub repository] (https://github.com/terkaterka/R-omics). You will find there
* my homeworks
* my first R package
* 


You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
